\chapter{Preparations}
\label{preparations}

All materials for the iOS part of this course are on iTunes U. Here's a link. Best is to subscribe to this online course in iTunes so it will automatically download new materials as they become available.

\href{https://itunes.apple.com/us/course/developing-ios-8-apps-swift/id961180099}{https:/\slash itunes.apple.com\slash us\slash course\slash developing-ios-8-apps-swift\slash id961180099}

So, many of the references in these iOS assignments are to materials form that course, like this one:

\begin{itemize}
\item Before you do anything else, watch \emph{Lecture 1} from the iTunes U series.

\end{itemize}

You'll need to start understanding object-oriented programming, because the iOS platform requires you to take an object-oriented approach when making apps!

\begin{itemize}
\item First, read up on Swift concepts. See \emph{Reading: Project 1}.

\item \href{http://www.raywenderlich.com/81952/intro-object-oriented-design-swift-part-1}{This document}\footnote{\href{http://www.raywenderlich.com/81952/intro-object-oriented-design-swift-part-1}{http:/\slash www.raywenderlich.com\slash 81952\slash intro-object-oriented-design-swift-part-1}} will help you understand that OO is trying to model ``the real world'' or whatever that is.

\end{itemize}

\chapter{Homework}
\label{homework}

One part of this class is starting to fully understand and develop valid requirements for your assignments. Make sure you read the requirements, understand them, ask questions if needed, and always re-check the requirements when you \emph{think} you're finished!

\begin{itemize}
\item Read the requirements for this week's assignment. See \emph{Programming: Project 1}.

\end{itemize}

\chapter{Assessment}
\label{assessment}

This first homework assignment will be graded \emph{in class} next week. You will need to show the app working on a real device.

Your work on this assignment will be evaluated along two axes primarily:

\begin{itemize}
\item \emph{Scope} -- to what extent does your code implement the features required by our specification?

\item \emph{Correctness} -- to what extent is your code free of bugs?

\end{itemize}
